Dependent Object Types

### 2012-08-27 doc/candidacy/report.tex
bib

\section{Survey of the Selected Papers}%: The Giants upon whose shoulders I will stand
% TODO
%Background --- Describe the three papers in detail, the problem they
%tackle, the solutions and results, and their shortcomings, and how they
%relate to your work.  This part builds the basis for the oral candidacy exam.

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{mittelbach}
F.~Mittelbach, M.~Goossens, J.~Braams, D.~Carlisle, and C.~Rowley, 
\emph{The {\LaTeX}} Companion, 2nd~ed.\hskip 1em plus
0.5em minus 0.4em\relax Addison-Wesley Professional, 2004.

\end{thebibliography}

>>>>

\section{Survey of the Selected Papers}%: The Giants upon whose shoulders I will stand

I present three papers~\cite{nuObj,tribe,homl}, each of which models a
calculus with path-dependent types.

% TODO
%Background --- Describe the three papers in detail, the problem they
%tackle, the solutions and results, and their shortcomings, and how they
%relate to your work.  This part builds the basis for the oral candidacy exam.

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{IEEEabrv,dot}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
%\begin{thebibliography}{1}

%\bibitem{mittelbach}
%F.~Mittelbach, M.~Goossens, J.~Braams, D.~Carlisle, and C.~Rowley, 
%\emph{The {\LaTeX}} Companion, 2nd~ed.\hskip 1em plus
%0.5em minus 0.4em\relax Addison-Wesley Professional, 2004.

%\end{thebibliography}
